\textbf{Autoreduction - an automated data reduction system for beamline instruments at the ISIS Facility}

### 2017-07-11 Documentation/paper/paper.tex
Updated description of message queue system

When the monitor detects that a new run has completed on an instrument, it sends a
request to do so to \emph{Data Ready}. The state database consumes the
request and creates a corresponding job in the database, before
sending a request to process it to \emph{Reduction Pending}. The reduction
worker takes this message and executes the appropriate reduction script, sending the
result to either \emph{Reduction Complete} or \emph{Reduction Error},
where it's consumed by the state database to update the status of the
job.

@@

Apache ActiveMQ\cite{activemq} is used as the message queueing system, with
message contents as JSON-formatted objects. The intention of the message
is conveyed by which queue it's placed in, rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature, which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

Data files at ISIS typically run in the hundreds of MB, so would be
impractical to send directly in a message; they're provided as file
paths on a shared file archive. Meanwhile, the reduction script to be
used is sent as a string; the script is served from the state database,
and using the message queue directly to send it obviates the need to
rely on a potentially flaky shared file store within the system.

@@

When a new run has been completed on the beam line, the raw data files are
placed in a shared filesystem. A node runs a Python watchdog daemon that
tracks changes in this filesystem, and when a new run is detected, sends a
message to \emph{Data Ready} with details of the run. The particular
choice of monitor isn't crucial; anything would work as long as it
pushed the same message to the queue. In the current production system
at ISIS, the run monitor is on same node as the state database itself.

>>>>

When the monitor detects that a new run has completed on an instrument, it will send a 
message to the \emph{Data Ready} queue. The \emph{QueueProcessor} process will consume this
message, strip out the relevant information and creates a corresponding job in the database.
\emph{QueueProcessor} will then send the message on to the \emph{Reduction Pending} queue.
The \emph{AutoreductionProcessor} process will be watching the \emph{Reduction Pending} queue.
When \emph{AutoreductionProcessor} recieves a message, it runs the \emph{PostProcessAdmin} 
script which will send a message to the \emph{ReductionStarted} queue such that the database
remains up to date. Once reduction has finished, \emph{PostProcessAdmin}  will send the
result to either \emph{Reduction Complete} or \emph{Reduction Error} where it will be consumed
by the \emph{QueueProcessor} and updated in the database.

@@

Apache ActiveMQ \cite{activemq} is used as the message queueing system using 
JSON-formatted objects as messages. The intention of the message
is conveyed by which queue it's placed in rather than a field in the
message itself. Runs can be `scheduled' simply by using ActiveMQ's
scheduled delay feature which allows a message to be delivered a given
time after it's been pushed to the queue.

@@

Data files at ISIS typically run in the hundreds of MB. They are therefore 
impractical to be sent directly in a message and instead they're provided as file
paths on a shared file archive. Meanwhile, the reduction script to be
used is sent as a string; the script is served from the state database
and using the message queue to directly send it obviates the need to
rely on a potentially flaky shared file store within the system.

@@

When a new run has been completed on the beam line, the raw data files are
placed in a shared filesystem. A node runs a Python watchdog daemon that
tracks changes in this filesystem and, when a new run is detected, will send a
message to \emph{Data Ready} with details of the run. The particular
choice of monitor isn't crucial; anything would work as long as it
pushed the same message to the queue. In the current production system
at ISIS, the run monitor is on same node as the state database itself.
